---
title: "Country with highest number of COVID-19 postive cases against number of tests"
output: html_document
---

## Introduction 

This is analysis tries to provde an answer to the question, "Which Countries have had the highest number of positive cases against the number of tests."
This datset was collected between the 20th of January 2020 and the 1st of June 2020.

#Import the dataset 
```{r}
library(tidyverse)

covid_df <- read.csv("covid19.csv")
```
Examining the features of the dataset
```{r}
dim(covid_df)
vector_cols <- colnames(covid_df)
typeof(vector_cols)
head(covid_df)
glimpse(covid_df)
```
A quick examination of the dataset shows the following:
The dataset comprises of 10903 rows and 14 columns
The data structure of the columns vector, vector_cols is a character.
The "Province_State" column has mixed data - for specific states and for country level. We will need to filter this column to be consistent with either State level or Country level.
```{r}
covid_df_all_states <- covid_df %>%
  filter(Province_State == "All States") %>%
  select(-Province_State)

view(covid_df_all_states)
```
Notice that some columns provide daily information and some provide cumulative information

```{r}
covid_df_all_states_daily <- covid_df_all_states %>%
  select(Date, Country_Region, active, hospitalizedCurr, daily_tested, daily_positive)
view(covid_df_all_states_daily)
```

Since our objective is the highest countries, we will extract the top ten cases countries data
```{r}
covid_df_all_states_daily_sum <- covid_df_all_states_daily %>%
  group_by(Country_Region) %>%
  summarize(
    tested = sum(daily_tested),
    positive = sum(daily_positive),
    active = sum(active),
    hospitalized = sum(hospitalizedCurr)
  ) %>%
  arrange(-positive) %>%


view(covid_df_all_states_daily_sum)

covid_top_10 <- head(covid_df_all_states_daily_sum, 10)
view(covid_top_10)
```

Which countries have had the highest number of positive cases against the number of tests?
##getting vectors
```{r}
countries <- covid_top_10$Country_Region
tested_cases <- covid_top_10$tested
positive_cases <- covid_top_10$positive
active_cases <- covid_top_10$active
hospitalized_cases <- covid_top_10$hospitalized
```
##naming the vectors
```{r}
names(tested_cases) <- countries
names(positive_cases) <- countries
names(active_cases) <- countries
names(hospitalized_cases) <- countries

positive_tested_top_3 <- positive_cases/tested_cases

view(positive_tested_top_3)

sort(positive_tested_top_3)
```
##creating vectors of top 3
```{r}
bangladesh <- c(0.15, 320834, 49531, 685992, 0)
united_kingdom <- c(0.11, 1473672, 166909, 0, 0)
united_states <- c(0.10, 17282363, 1877179, 0, 0)
```
##create a matrix to combine the vectors
```{r}
covid_mat <- rbind(bangladesh, united_kingdom, united_states)
colnames(covid_mat) <- c("Ratio", "tested", "positive", "active", "hospitalized")

view(covid_mat)
```
##Results
```{r}
question <- "which countries haev had the highest number of positive cases against the number of tests?"
answer <- c("Positive tested cases" = positive_tested_top_3)

datasets <- list(
  original = covid_df,
  allstates = covid_df_all_states,
  daily = covid_df_all_states_daily,
  top_10 = covid_top_10
)

matrices <- list(covid_mat)

vectors<- list(vector_cols, countries)

data_structure_list <- list("dataframe" = datasets, "matrix" = matrices, "vector" = vectors)

covid_analysis_list <- list(question, answer, data_structure_list)

covid_analysis_list[[2]]
```

#Conclusion
Following from the analysis, within the range of the dataset, from January 20, 2020 - June 2020, Bangladesh had the highest number of positive cases against the number of tests conducted, followed by the United Kingdom and the United States, respectively.
Over the years to present-day, more data has been obtained and further insights can be derived from more recent and updated dataset https://www.kaggle.com/lin0li/covid19testing
